Queue Aware Precoder Design for Space Frequency Resource Allocation

### 2014-07-17 Report/introduction.tex
phase-1

In the traditional \ac{WSRM} formulation, the precoders are designed for the sub-channels independently due to the interference-free \ac{OFDM} transmission. In this work, since the objective is to identify the transmission rates for all the users across the space-frequency resources, the precoders are to be designed jointly across the space-frequency dimension. In order minimize the number of queued packets at the \acp{BS}, the precoders are designed by the proposed \ac{JSFRA} formulation with two different approaches in a centralized manner. We also propose the distributed approaches for the centralized problem for designing the precoders independently across the \acp{BS} with the limited information exchange.

>>>>

In the traditional \ac{WSRM} formulation, the precoders are designed for the sub-channels independently due to the interference-free \ac{OFDM} transmission. In this work, since the objective is to identify the transmission rates for all the users across the space-frequency resources, the precoders are to be designed jointly across the space-frequency dimension. In order minimize the number of queued packets at the \acp{BS}, the precoders are designed by the proposed \ac{JSFRA} formulation with two different approaches in a centralized manner. We also propose distributed approaches for the centralized problem for designing the precoders independently across the \acp{BS} with the limited information exchange.

### 2014-07-17 Report/simulation_distributed.tex
phase-1

In this section, we discuss the simulation performances of the algorithms briefed in Section \ref{sec-3} and \ref{sec-4}. The comparison studies are made using the queue deviation and sum rate convergence using various system models. The distributed algorithms for the \ac{JSFRA} scheme and the equivalent \ac{MSE} representation are compared using the excess backlogged packets present after each \ac{SCA} update.

Fig. \ref{fig-d-1} demonstrates the performance of the distributed algorithms in an \ac{OFDM} framework modeled with \me{N = 3} sub-channels with \me{N_B = 2} \acp{BS}, each equipped with \me{N_T = 4} transmit antennas. Each \ac{BS} serves \me{|\mc{U}_b| = 4, \forall b \in \{1,2\}} users in a coordinated manner to reduce the number of backlogged packets at each \ac{BS}. Fig. \ref{fig-d-1.1} shows the total number of backlogged packets  and Fig. \ref{fig-d-1.2} plots the total rate achieved by different algorithms after each \ac{SCA} update. As pointed out earlier, the distributed algorithms are very much dependent on the choice of the step size used to update the subgradients. In particular, the primal decomposition is more susceptible to the step size as compared to the \ac{ADMM} approach, since interference values are fixed for each primal exchange, it may lead to infeasible solutions if the initial or any intermediate update on the interference determined by \eqref{primal-sg-update} are not in the valid range.

Fig. \ref{fig-d-1} also compares the performance of the iterative algorithm for \ac{JSFRA} scheme via \ac{MSE} reformulation using the \ac{KKT} conditions discussed in Section \ref{sec-4.3}. The performance is inferior compared to the other algorithms due to the violation in the assumptions made in the algorithm design \textit{i.e}, \me{Q_k \gg t_k}. Since in this case, we are comparing the \me{q = 1} case, the queue condition \me{Q_k \gg t_k} needs to be satisfied in order to remove the absolute operator from the expression in \eqref{eqn-9.1a} to form \eqref{kkt-mse-1.1}. The total number of backlogged packets after the each iteration reduces monotonically in all cases and converges to the points closer to the centralized solution \me{\chi = 33} bits. As seen in Fig. \ref{fig-d-1}, the \ac{ADMM} approach provides better convergence compared to the primal approach in the initial phase due to the quadratic penalty term included in the objective, which gets pronounced initially due to the large deviation between the assumed and the actual interference across the coordinating \acp{BS}.
\begin{figure*}
\centering
\begin{subfigure}{0.49\textwidth}
\includegraphics[width=\columnwidth]{fig-3}
\caption{Queue deviation}
\label{fig-d-1.1}
\end{subfigure}
\hfill
\begin{subfigure}{0.49\textwidth}
\includegraphics[width=\columnwidth]{fig-4}
\caption{Sum rate performance}
\label{fig-d-1.2}
\end{subfigure}
\caption[short]{Convergence plot for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 3,2,8,1 \rbrace} model}
\label{fig-d-1}
\end{figure*}

In Fig. \ref{fig-d-2}, the total backlogged packets and the sum throughput offered to minimize the number of queued packets for \me{K = 12} users across \me{N = 5} sub-channels are plotted for the analysis. The system considers \me{N_B = 3} \acp{BS}, each having \me{N_T = 4} transmit antennas serving \me{|\mc{U}_b| = 4} users mounted with \me{N_R = 2} antennas respectively. The users are assumed to be scattered over the cell boundary with the maximum interference power from any neighboring \ac{BS} follows \me{\mathbb{U}(0,-6)} dB independently. The sum rate and queue minimizing behavior follows similar pattern as in Fig. \ref{fig-d-1} for \me{N_B = 2} \acp{BS} scenario.

Fig. \ref{fig-d-2} demonstrates the convergence behavior of the different distributed algorithms discussed so far. It can be seen from Fig. \ref{fig-d-2}, that the distributed algorithms depend on the step size used in the subgradient update procedure. The primal decomposition algorithm, which distributes the precoder design by fixing the interference thresholds at each iteration, converges to the optimal resource allocations gradually as compared to the \ac{ADMM} based dual approach. The \ac{ADMM} scheme depends on the step size for the convergence, where the larger step size makes the algorithm to reach the optimal point quickly but takes more iterations to converge. The choice of \me{I_{\max}}, which denotes the maximum \ac{SCA} iterations, and the \me{J_{\max}}, which denotes the subgradient convergence limit, are fixed at \me{100} and \me{8} respectively. The information exchange is made at each instant and the performances are evaluated as if the actual transmission is happened with the precoders \me{\mvec{m}{l,k,n}^{(i)}} designed at the \me{\ith{i}} instant in a distributed manner. In this paper, we assume that the actual transmission will happen at the end of the precoder convergence or when the maximum number of iterations reached.

The performance of the joint \ac{Q-WSRM} scheme discussed in the Section \ref{sec-3.1} performs slightly worse than (\me{\approx \, 2} bits) the \ac{JSFRA} scheme in reducing the number of queued packets, even though the performance were similar in Table \ref{tbl-1}. As stated earlier, the joint \ac{Q-WSRM} scheme and the \ac{JSFRA} scheme with the exponent \me{q = 1} performs the same when the number of queued packets are identical for all the users. In this case, the joint \ac{Q-WSRM} becomes the sum rate maximization problem which is equivalent to the greedy \me{q=1} \ac{JSFRA} scheme. In the current scenario, since the number of queued packets are different for the users, the performance of the \ac{JSFRA} scheme is better due to its greedy resource allocation. It can be seen from Fig. \ref{fig-d-2}, that the \ac{KKT} based approach provides inferior result in the queue minimization perspective as compared with the sum rate plot. The performance degradation is due to the unconstrained rate increase for the users beyond their actual number of queued packets available to transmit. Since the objective uses the \me{\ell_1} minimization, the \ac{KKT} solution is not optimal unless the queues are far greater than the transmission rate available for each user. The number of queued packets are initialized in a way to analyze the effect of the unconstrained behavior in the \ac{KKT} scheme.
\begin{figure*}
\centering
\begin{subfigure}{0.49\textwidth}
\includegraphics[width=\textwidth]{NewFigures/distributed_queue_plot_1}
\caption{Queue deviation}
\end{subfigure}
\hfill
\begin{subfigure}{0.49\textwidth}
\includegraphics[width=\textwidth]{NewFigures/distributed_sum_rate_plot_1}
\caption{Sum rate performance}
\end{subfigure}
\caption{Convergence plot for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 2,3,9,2 \rbrace} model}
\label{fig-d-2}
\end{figure*}

The performance of the \ac{MSE}-\ac{KKT} scheme is shown in comparison with the other schemes discussed so far in Fig. \ref{fig-d-3}. It can be seen that the \ac{KKT} based approach performs similar to the optimization problem given in \eqref{eqn-9}, which is solved using the solver \cite{grant2008cvx}. In the \me{\ell_2} case, the objective is differentiable and hence can be differentiable for any number of queued packets as compared to the \me{\ell_1} case requiring larger queue sizes in order to drop the absolute function occurring in the norm operator. The performance of the closed form solution using the \ac{KKT} solution achieves similar performance without allocating rates beyond the available queued packets. In order to bring out the performance difference, \me{\ell_1} objective plot is also provided in Fig. \ref{fig-d-3} providing better reduction in the number of queued packets in the current transmission slot.
Fig. \ref{fig-d-3}
\begin{figure*}
\centering
\begin{subfigure}{0.49\textwidth}
\includegraphics[width=\textwidth]{fig-7}
\caption{Queue deviation}
\end{subfigure}
\hfill
\begin{subfigure}{0.49\textwidth}
\includegraphics[width=\textwidth]{fig-8}
\caption{Sum rate performance}
\end{subfigure}
%\caption{Convergence plot for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 6,3,12,1 \rbrace} model}
\caption{Convergence plot for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 4,2,12,1 \rbrace} model}
\label{fig-d-3}
\end{figure*}

>>>>

The performance of the distributed algorithms are studied in this section by comparing with the centralized algorithms. The total number of queued packets after the current allocation and the total sum rate achieved by the network are used as the performance measures. Fig. \ref{fig-d-1} shows the performance of the algorithms for the system configuration represented by \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 3,2,8,1 \rbrace} with \me{N_T = 4} transmit antennas at each \ac{BS}. Each \ac{BS} serves \me{|\mc{U}_b| = 4} users in a coordinated manner to reduce the total number of backlogged packets at each \ac{BS}. Fig. \ref{fig-d-1.1} shows the total number of backlogged packets  and Fig. \ref{fig-d-1.2} plots the total rate achieved by different algorithms after each \ac{SCA} update. As pointed out in Section \ref{sec-4}, the performance and the convergence speed of the distributed algorithms are susceptible to the choice of the step size used in the subgradient update. Since the interference values are fixed for local subproblem in the primal approach, it may lead to infeasible solutions if the initial or any intermediate update using \eqref{primal-sg-update} is not valid.

The Fig. \ref{fig-d-1} plots the performance of the primal and the \ac{ADMM} solutions of the \ac{JSFRA} scheme using \ac{SCA} and by \ac{MSE} relaxation at each \ac{SCA} update points. In between the \ac{SCA} updates, the primal or the \ac{ADMM} schemes are performed for \me{J_{\max} = 20} iterations by exchanging either the fixed interference variables in the primal approach or the dual variables in the \ac{ADMM} scheme. It can be seen from Fig. \ref{fig-d-1} that the distributed algorithms approaches the centralized performance by exchanging minimal information between the coordinating \acp{BS}. The plot also includes the \ac{Q-WSRM} which performs similar to the other centralized schemes discussed in this paper.
\begin{figure*}
\centering
\begin{subfigure}{0.49\textwidth}
\includegraphics[width=\columnwidth]{fig-3}
\caption{Queue deviation}
\label{fig-d-1.1}
\end{subfigure}
\hfill
\begin{subfigure}{0.49\textwidth}
\includegraphics[width=\columnwidth]{fig-4}
\caption{Sum rate performance}
\label{fig-d-1.2}
\end{subfigure}
\caption[short]{Convergence plot for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 3,2,8,1 \rbrace} model}
\label{fig-d-1}
\end{figure*}

In Fig. \ref{fig-d-2}, the performance of the distributed algorithms are studied for \me{K = 12} users utilizing \me{N = 6} sub-channels. The system considers \me{N_B = 3} \acp{BS}, each having \me{N_T = 4} transmit antennas serving \me{|\mc{U}_b| = 4} users equipped with \me{N_R = 2} antennas respectively. The users are assumed to be scattered over the cell boundary with the maximum interference power from any neighboring \ac{BS} follows \me{\mathbb{U}(0,-6)} dB. The performance of the algorithms are similar to the \me{N_B = 2} \ac{BS} scenario discussed earlier.

Fig. \ref{fig-d-2} plots the performance of the centralized and the distributed algorithms at each \ac{SCA} update. In case of the distributed algorithms, in between each \ac{SCA} update, the primal or the \ac{ADMM} exchanges are performed for \me{J_{\max} = 20} iterations. In practice, \me{J_{\max} = 1} can be set to perform the \ac{SCA} update, \ac{ADMM} or primal update, and the receive beamformer \me{\mvec{W}{k,n}} update at the same instant. The data tips are used to highlight the convergent points of various algorithms. The performance of the \ac{JSFRA} schemes using the primal decomposition are notably inferior compared to the \ac{ADMM} approach for the same schemes. It is mainly attributed to the difficulty in selecting the step size for the system employing \me{N_B \geq 3} \acp{BS}.
\begin{figure*}
\centering
\begin{subfigure}{0.49\textwidth}
\includegraphics[width=\textwidth]{fig-5}
\caption{Queue deviation}
\end{subfigure}
\hfill
\begin{subfigure}{0.49\textwidth}
\includegraphics[width=\textwidth]{fig-6}
\caption{Sum rate performance}
\end{subfigure}
\caption{Convergence plot for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 6,3,12,2 \rbrace} model}
\label{fig-d-2}
\end{figure*}

The performance of the \ac{MSE}-\ac{KKT} scheme discussed in Section \ref{sec-4.3} is presented in Fig. \ref{fig-d-3}. It compares the \ac{JSFRA} scheme with \me{\ell_1} and \me{\ell_2} norm cases in addition to the \ac{Q-WSRM} scheme. We compare the performance of the \ac{MSE}-\ac{KKT} scheme for the exponents \me{q=1} and \me{q=2}. The performance of the \me{\ell_1} \ac{JSFRA} scheme performs the best over other algorithms in minimizing the total number of queued bits after the current allocation due to its greedy approach. The inclusion of the additional second order rate term in \eqref{pf-1}, the \me{\ell_2} \ac{JSFRA} scheme achieves different performance than the \ac{Q-WSRM} scheme as shown in Fig. \ref{fig-d-3}.

It can be seen from Fig. \ref{fig-d-3.2}, that the sum rate of the \me{q=1} \ac{KKT} approach outperforms other schemes in spite of Fig. \ref{fig-d-3.1} showing inferior queue minimizing performance. This due to the lack of the rate bounding constraint \eqref{kkt-mse-4.2}, which is simply given by \me{\sigma_{l,k,n}^{(i)} = \frac{a_k}{\log(2)}} providing no control for the excess allocations. For \me{q=2}, when the allocated rate exceeds the available queued bits, \me{\sigma_{l,k,n}^{(i)}} will be negative, thereby reducing \eqref{kkt-mse-4.1} as \me{\alpha_{l,k,n}^{(i)} < \alpha_{l,k,n}^{(i-1)}} to reduce the priority for the corresponding user in the next iteration. The performance of the closed form solution using the \ac{KKT} solution performs similar to the centralized schemes with \me{q=2} by limiting the rates beyond the available queued packets.
\begin{figure*}
\centering
\begin{subfigure}{0.49\textwidth}
\includegraphics[width=\textwidth]{fig-9}
\caption{Queue deviation}
\label{fig-d-3.1}
\end{subfigure}
\hfill
\begin{subfigure}{0.49\textwidth}
\includegraphics[width=\textwidth]{fig-10}
\caption{Sum rate performance}
\label{fig-d-3.2}
\end{subfigure}
%\caption{Convergence plot for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 6,3,12,1 \rbrace} model}
%\caption{Convergence plot for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 4,2,12,1 \rbrace} model}
\caption{Convergence plot for \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 4,2,12,1 \rbrace} model}
\label{fig-d-3}
\end{figure*}

### 2014-07-17 Report/simulation_results.tex
ver_0.0.1
modified for KKT MMSE
phase-1

In this section, we discuss the performance of the above mentioned algorithms in different scenarios on minimizing the number of queued packets at the transmitter. To begin with, we consider a single cell \ac{SISO} system operating at \me{10} dB \ac{SNR} with \me{K = 3} users sharing \me{N = 3} sub-channel resources. The number of packets waiting at the transmitter is kept as \me{Q_k = 6} bits. With these assumptions, the resources allocated for the users on each sub-channel by various algorithms are listed in Table \ref{tbl-1}.

Table \ref{tbl-1} shows the channel seen by the users over each sub-channel followed by the rates allocated over each sub-channel by three different algorithms, joint \ac{Q-WSRM} allocation without the maximum rate constraints \eqref{eqn-3.1.4}, \ac{JSFRA} scheme and the band-wise \ac{Q-WSRM} scheme. Since the total allowed transmission constraint is present only on the \ac{JSFRA} scheme, the total number of packets remained after the current transmission slot is minimum for the \ac{JSFRA} scheme with \me{1.14} bits, where \me{\chi = \sum_{k = 1}^K \; [ Q_k - t_k ]^+}. The precoder design for the optimal allocation in band-wise \ac{Q-WSRM} depends on the order of selecting the sub-channels, which leads to an exhaustive search. In this scenario, the formulation in \eqref{q_gen_sum} and \eqref{gen_sum} performs the same as compared to the \ac{JSFRA} scheme, \textit{i.e}, with the maximum rate constraints, the joint \ac{Q-WSRM} scheme performs the same as the \ac{JSFRA} scheme.

\begin{table*}
\centering
\renewcommand{\arraystretch}{1.25} \scriptsize
\begin{tabular}{|*{14}{c|}}
\hline
\multirow{2}{*}{Users} & \multirow{2}{*}{Queued} & \multicolumn{3}{c|}{\multirow{2}{*}{Channel Gains}} & \multicolumn{3}{c|}{Joint Q-WSRM w/o} & \multicolumn{3}{c|}{\multirow{2}{*}{JSFRA Scheme}} & \multicolumn{3}{c|}{WSRM band} \\
\multirow{2}{*}{} & \multirow{2}{*}{Packets} & \multicolumn{3}{c|}{} & \multicolumn{3}{c|}{Queue constraints \eqref{eqn-3.1.4}} & \multicolumn{3}{c|}{} & \multicolumn{3}{c|}{Alloc Scheme} \\
\cline{3-14}
 && Sch-\me{1} & Sch-\me{2} & Sch-\me{3} & Sch-\me{1} & Sch-\me{2} & Sch-\me{3} & Sch-\me{1} & Sch-\me{2} & Sch-\me{3} & Sch-\me{1} & Sch-\me{2} & Sch-\me{3} \\
\hline
\me{1} & \me{6} & \me{2.26} &  \me{0.69}  &  \me{0.73} & \me{0} &  \me{0}  &  \me{0} & \me{5.56} &  \me{0}  &  \me{0} & \me{0} &  \me{0}  &  \me{2.68} \\
\me{2} & \me{6} & \me{0.53} &  \me{1.93}  &  \me{1.40} & \me{0} &  \me{5.29}  &  \me{0} & \me{0} &  \me{5.33}  &  \me{0} & \me{0} &  \me{5.26}  &  \me{0} \\
\me{3} & \me{6} & \me{2.45} &  \me{1.31}  &  \me{2.42} & \me{5.84} &  \me{0}  &  \me{5.95} & \me{0} &  \me{0}  &  \me{5.95} & \me{5.93} &  \me{0}  &  \me{0} \\
\hline
\multicolumn{5}{|c|}{Remaining backlogged packets (\me{\chi})} & \multicolumn{3}{c|}{\me{6.70} bits} & \multicolumn{3}{c|}{\me{1.14} bits} & \multicolumn{3}{c|}{\me{4.11} bits} \\
\hline
\end{tabular}
\caption{Sub channel wise allocation for a scheduling instant}
\label{tbl-1}
\end{table*}

In order to understand the behavior in a \ac{MIMO} framework, we consider a system with \me{N=3} sub-channels and \me{N_B = 2} \acp{BS}, each equipped with \me{N_T = 4} transmit antennas operating at \me{10}dB \ac{SNR}, serving \me{K = 8} users with \me{N_R} antennas each. The users are assumed to be at the cell-edge with the maximum interference seen from the neighboring \acp{BS} is limited to \me{-3} dB and each \ac{BS} are associated with \me{|\mc{U}_b|} users respectively.

\begin{figure*}
\centering
\begin{subfigure}{0.49\textwidth}
\includegraphics[width=1.0\textwidth]{NewFigures/centralized-1a}
\caption{\me{4 \times 1} system}
\label{fig-1}
\end{subfigure}
\hfill
\begin{subfigure}{0.49\textwidth}
\includegraphics[width=1.0\textwidth]{NewFigures/centralized-2a}
\caption{\me{4 \times 2} system}
\label{fig-2}
\end{subfigure}
\caption{Convergence plot for \me{\lbrace N,N_B,K \rbrace = \lbrace 3,2,8 \rbrace} model}
\end{figure*}

Fig. \ref{fig-1} shows the performance of the above discussed schemes for a single receive antenna system. The figure compares the total number of \ac{SCA} iterations required by the \ac{JSFRA}, \ac{JSFRA} with sum power constraint, \ac{SRA} and \ac{Q-WSRM} schemes to achieve the optimal resource allocation to minimize the number of backlogged packets during the given scheduling instant. The convergence of the proposed \ac{JSFRA} is much quicker compared to the band-wise allocation schemes like the \ac{Q-WSRM} and the \ac{SRA} schemes. The waterfall like behavior for the band-wise allocation schemes suggests the rapid convergence when there is a band switch over, \textit{i.e}, when the queues are updated from the earlier sub-channels to find the precoders for the current sub-channel. The convergence at each sub-channel is iterated for the accuracy of \me{\approx 10^{-4}} or for a predetermined count \me{I_{\max}}, which creates the flat region between each waterfall behavior. The backlogged bits and the iteration count by various schemes at the convergence point are marked in the figures using data tips.
\begin{table}
\centering
\renewcommand{\arraystretch}{1.25} \scriptsize
\begin{tabular}{|c|*{8}{c}|c|}
\hline
\me{q} & \multicolumn{8}{c|}{user indices} & \me{\chi} \\
\hline
\me{1} & 12.0 &  6.15 &  5.32 & 12.0 &  6.95 & 11.1 & 11.9 & 10.8 & 19.71 \\
\me{2} & 11.9 & 7.3 & 5.9 & 10.1 & 9.19 & 10.1 & 10.8 & 10.3 & 20.48 \\
\me{\infty} & 9.15 & 9.15 & 9.15 & 9.15 & 9.16 & 9.15 & 9.15 & 9.15 & 22.75 \\
\hline
\end{tabular}
\caption{Queue information for \me{N=5} sub-channels}
\label{tbl-3}
\end{table}

Fig. \ref{fig-2} compares the convergence behavior of the precoder designs, which allocates the space-frequency resources to the users to minimize the number of backlogged packets. Different values for the exponent \me{q} are compared in Table \ref{tbl-3} for the system configuration \me{\{N_B,K,N_T,N_R\}= \{2,8,4,1\}}. The number of backlogged packets at each user before the current scheduling is fixed to be \me{12} bits. It is evident that the exponent \me{q=1} shows the greedy resource allocation in comparison with the fair scheduling achieved using \me{q=\infty}. The \me{q=\infty} norm does the fair scheduling even the path loss experienced by the users are different. It tries to minimize the variance across the backlogged packets of each user present in the system.

>>>>

This section discusses the performance of the centralized algorithms discussed in Section \ref{sec-3} for a few system configurations. To begin with, we consider a single cell \ac{SISO} model operating at \me{10} dB \ac{SNR} with \me{K = 3} users sharing \me{N = 3} sub-channel resources. The number of packets waiting at the transmitter for each user is given by \me{Q_k = 5,8} and \me{6} bits respectively. With this configuration, the resources allocated for the users on each sub-channel by various algorithms are listed in Table \ref{tbl-1}.

Table \ref{tbl-1} lists the sub-channel wise channel seen by the users followed by the assigned rates over each sub-channel by three different algorithms, \ac{Q-WSRM} allocation, \ac{JSFRA} scheme and the band-wise \ac{Q-WSRM} scheme using \ac{WMMSE} precoder design proposed in \cite{wmmse_shi}. The performance metric used for the comparison of different algorithms is the total number of backlogged bits left over at each slot after the allocation, which is denoted by \me{\chi = \sum_{k = 1}^K \; [ Q_k - t_k ]^+}. It can be seen from Table \ref{tbl-1}, that the \ac{Q-WSRM} scheme provides more priority to the third user with \me{Q_{3} = 6} bits compared to the first user with \me{Q_{1} = 5} bits while allocating the first sub-channel. Int contrast to the \ac{Q-WSRM} scheme, the \ac{JSFRA} scheme assigns the first user on the first sub-channel thereby reducing the total number of backlogged packets waiting at the transmitter.
\begin{table*}
\centering
\renewcommand{\arraystretch}{1.25} \scriptsize
\begin{tabular}{|*{14}{c|}}
\hline
\multirow{2}{*}{Users} & \multirow{2}{*}{Queued} & \multicolumn{3}{c|}{\multirow{2}{*}{Channel Gains}} & \multicolumn{3}{c|}{Q-WSRM approach} & \multicolumn{3}{c|}{\multirow{2}{*}{JSFRA Scheme}} & \multicolumn{3}{c|}{Q-WSRM band} \\
\multirow{2}{*}{} & \multirow{2}{*}{Packets} & \multicolumn{3}{c|}{} & \multicolumn{3}{c|}{(\emph{backpreassure} algorithm)} & \multicolumn{3}{c|}{} & \multicolumn{3}{c|}{Alloc Scheme} \\
\cline{3-14}
 && Sch-\me{1} & Sch-\me{2} & Sch-\me{3} & Sch-\me{1} & Sch-\me{2} & Sch-\me{3} & Sch-\me{1} & Sch-\me{2} & Sch-\me{3} & Sch-\me{1} & Sch-\me{2} & Sch-\me{3} \\
\hline
\me{1} & \me{5} & \me{1.71} &  \me{0.53}  &  \me{0.56} & \me{0} &  \me{0}  &  \me{0} & \me{4.91} &  \me{0}  &  \me{0} & \me{0} &  \me{0}  &  \me{0} \\
\me{2} & \me{8} & \me{0.39} &  \me{1.41}  &  \me{1.03} & \me{0} &  \me{4.46}  &  \me{3.54} & \me{0} &  \me{4.36}  &  \me{0} & \me{0} &  \me{4.39}  &  \me{3.53} \\
\me{3} & \me{6} & \me{2.34} &  \me{1.26}  &  \me{2.32} & \me{5.72} &  \me{0}  &  \me{0} & \me{0} &  \me{0}  &  \me{5.79} & \me{5.81} &  \me{0}  &  \me{0} \\
\hline
\multicolumn{5}{|c|}{Remaining backlogged packets (\me{\chi})} & \multicolumn{3}{c|}{\me{5.28} bits} & \multicolumn{3}{c|}{\me{3.91} bits} & \multicolumn{3}{c|}{\me{5.28} bits} \\
\hline
\end{tabular}
\caption{Sub channel wise allocation for a scheduling instant}
\label{tbl-1}
\end{table*}

In order to understand the behavior in a \ac{MIMO} framework, we consider a system with \me{N=3} sub-channels and \me{N_B = 3} \acp{BS}, each equipped with \me{N_T = 4} transmit antennas operating at \me{10}dB \ac{SNR}, serving \me{|\mc{U}_b| = 3} users each. The users are located with the maximum interference seen from the neighboring \acp{BS} is limited to \me{-6} dB, thereby simulating a realistic scenario. Fig. \ref{fig-1} shows the performance of the centralized schemes for a single receive antenna system. It compares the total number of \ac{SCA} updates required by the \ac{JSFRA}, \ac{SRA} and the \ac{Q-WSRM} schemes to perform the optimal allocations to minimize the total number of backlogged packets.
\begin{figure*}
\centering
\begin{subfigure}{0.49\textwidth}
\includegraphics[width=1.0\textwidth]{fig-1-1}
\caption{\me{4 \times 1} system}
\label{fig-1}
\end{subfigure}
\hfill
\begin{subfigure}{0.49\textwidth}
\includegraphics[width=1.0\textwidth]{fig-2-1}
\caption{\me{4 \times 2} system}
\label{fig-2}
\end{subfigure}
\caption{Convergence plot for \me{\lbrace N,N_B,K \rbrace = \lbrace 3,3,9 \rbrace} model}
\end{figure*}

In the sub-channel wise allocations, where the total transmit power is shared equally among the sub-channels, the precoders are designed for each sub-channels independently. In this approach, the precoders are coupled via the number of queued bits which are updated using \eqref{eqn-weight} before designing the precoders for the sub-channels. At each \ac{SCA} points, the number of queued bits are reduced significantly with the introduction of a new sub-channel since the algorithm starts with a random inital point before it converges to an optimal\footnote{due to the nonconvex nature of the original problem} precoders. The total number of backlogged bits at each \ac{SCA} update instant are plotted in Fig. \ref{fig-1} for the discussed centralized schemes and the convergence point are marked with the data tips. Fig. \ref{fig-2} compares the performance of the centralized algorithms for the \me{N_R = 2} receive antennas.
\begin{table}
\centering
\renewcommand{\arraystretch}{1.25} \scriptsize
\begin{tabular}{|c|*{8}{c}|c|}
\hline
\me{q} & \multicolumn{8}{c|}{user indices} & \me{\chi} \\
\hline
\me{1} & 15.00 & 3.95 & 5.26 & 8.95 & 7.03 & 11.90 & 12.00 & 9.73 & 25.15 \\
\me{2} & 11.23 & 3.93 & 10.76 & 10.65 & 10.27 & 9.68 & 8.77 & 5.90 & 27.77 \\
\me{\infty} & 11.41 & 4.41 & 10.41 & 10.41 & 10.41 & 8.41 &  8.41 &  6.41 & 28.68 \\
\hline
\me{Q_k}  & 15.0 &  8.0 &  14.0 & 14.0 &  14.0 & 12.0 & 12.0 & 10.0  \\    
\cline{1-9}
\end{tabular}
\caption{Queue information for the system \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 5,2,8,1 \rbrace}}
\label{tbl-3}
\end{table}

The behavior of the \ac{JSFRA} algorithm for different exponents \me{q} are outlined in the Table \ref{tbl-3} for the users located at the cell-edge of the system employing \me{N_T = 4} transmit antennas. The configuration is mentioned in the caption of Table \ref{tbl-3} along with the number of queued bits for each user. It is evident that the algorithm minimizes the queued bits for the \me{\ell_1} norm compared to the \me{\ell_2} norm, which is shown in the column displaying the total number of left over packets \me{\chi} in bits. The \me{\ell_{\infty}} norm provides fair allocation of the resources by making the left over packets \me{\chi_k = 3.58} bits. The \me{\ell_{\infty}} norm provides the fair allocation by making the queued deviation equal for all the users after the current allocation irrespective of their channel gains.
